LSOA domestic Electricty and Gas maps

### 2021-09-16 LSOA domestic Elec and Gas.Rmd
added OAC codes to elec consumption to check against age plot

>>>>

```{r ageOACAndElec}
# uses data.table for data load & matching (could be done with readr & dplyr etc)
library(data.table)
# you'll need this data (on sharepoint)
oacDT <- data.table::fread(paste0(dataFolder, "oac/lsoa-oac-data.csv"))
oacDT$la_name <- oacDT$`LA Name`
oacDT$LSOA11CD <- oacDT$`SOA Code`

solent_oacDT <- getSolent(oacDT)
Solent_2019DT <- data.table::as.data.table(Solent_2019)
setkey(Solent_2019DT, LSOA11CD)
setkey(solent_oacDT, LSOA11CD)

dt <- Solent_2019DT[solent_oacDT]

ggplot(dt, aes(x= 100 * prop_65m, 
                   y= mean_de2019, 
                   colour = la_name)) + # use colour for each LA
  geom_point() +
  #theme(legend.position = "None") + # otherwise we get the colour legend at the side
  labs(x = "% aged > 65, 2011 Census",
       y = "Domestic Electricity COnsumption") +
  facet_wrap(. ~ `Supergroup Name`) # draws a separate plot for each LA (in a different colour)
```
